SAT Competition 2020\tnoteref{title}

### 2020-12-17 paper/main.tex

With a few exceptions, progress in SAT solvers emerged as extensions or forks from existing code bases. 
One well-known tree of development is rooted in the Codebase of the Minisat solver by Niklas Éen and Niklas Sörenson~\cite{}. 
The most well-known fork of Minisat is the Glucose solver by Gilles Audemard and Laurent Simon~\cite{}.  
The authors of Glucose introduced numerous implementations of successful new methods, e.g., Literal Block Distance (LBD)~\cite{}, which they recently summarized in~\cite{}.

The SAT solver RISS by Norbert Manthey is a successful and award winning fork of Glucose (version 2.2) in combination with the state-of-the-art preprocessor Coprocessor~\cite{}.

Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh~\cite{}. 
Maple first emerged as a series of forks submitted to SAT Competition 2016, introducing the two new branching heuristics Learning Rate based Branching (LRB) and Conflict History based Branching (CHB)~\cite{}. 
The then award winning variant MapleCOMSPS is an implementation of the LRB heuristic on top of CoMinisatPS~\cite{}. 
The next award winning derivative Maple\_LCM\_Dist in SAT Competition 2017 came with a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}. 
Its extension MapleLCMDistChronoBT-DL with a new clause learning/forgetting heuristic Duplicate Learnts (DL)~\cite{} won SAT Race 2019. 
The success story of Maple resulted also in numerous submissions of modified Maple solvers in this competition, some of which have been successful (see Section~\ref{}).

>>>>

With a few exceptions, progress in SAT solvers emerged as extensions or forks from existing code bases. 
One well-known tree of development is rooted in the Codebase of the Minisat solver by Niklas Éen and Niklas Sörenson~\cite{Niklas:2003:Minisat}. 
The most well-known fork of Minisat is the Glucose solver by Gilles Audemard and Laurent Simon~\cite{Audemard:2018:Glucose}. 
It introduced numerous implementations of successful new methods, e.g., Literal Block Distance (LBD)~\cite{Audemard:2009:Glucose}. 
The SAT solver RISS by Norbert Manthey is a successful and award winning fork of Glucose (version 2.2) in combination with the state-of-the-art preprocessor Coprocessor~\cite{Manthey:2012:Coprocessor2}.

Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh introducing three-tier clause-managment~\cite{Oh:2015:satunsat}. 
Maple first emerged as a series of forks submitted to SAT Competition 2016 implementing new innovative branching heuristics on top of available code-bases~\cite{Liang:2016:LRB}. 
The then award winning variant MapleCOMSPS is an implementation of the new branching heuristics Learning Rate based Branching (LRB) on top of CoMinisatPS~\cite{Liang:2016:MapleCOMSPS}. 
The next award winning derivative Maple\_LCM\_Dist in SAT Competition 2017 came with a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}. 
Its extension MapleLCMDistChronoBT-DL with a new clause learning/forgetting heuristic Duplicate Learnts (DL)~\cite{} won SAT Race 2019. 
The success story of Maple resulted also in numerous submissions of modified Maple solvers in this competition, some of which have been successful (see Section~\ref{}).
